%%%%
% Sample Resume (Anonymized)
%%%%

\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{tabularx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}
\renewcommand\labelitemi{--}

\begin{document}

\documentTitle{John Doe}{
  \href{tel:9999999999}{\faPhone\ 9999999999} ~ | ~
  \href{mailto:john.doe@example.com}{\faEnvelope\ john.doe@example.com} ~ | ~
  \href{https://linkedin.com/in/johndoe}{\faLinkedin\ linkedin.com/in/johndoe} ~ | ~
  \href{https://github.com/johndoe}{\faGithub\ github.com/johndoe}
}

\tinysection{Summary}
Experienced Site Reliability Engineer with expertise in cloud infrastructure, observability, and automation.

\section{Skills}
\begin{tabularx}{\linewidth}{@{}lX@{}}
\textbf{Languages} & Python, Bash \\
\textbf{Automation} & Ansible, Python \\
\textbf{Cloud} & GCP, AWS, Azure \\
\textbf{OS} & Windows, Linux (Ubuntu, RHEL) \\
\textbf{Policies} & SOC2, GDPR \\
\textbf{Tools \& Platform} & Docker, Kubernetes (EKS, GKE, AKS), Helm, Terraform (IaC), Git, GitHub Actions, GitLab CI, Argo CD, JFrog Artifactory, SonarQube, Jenkins, Spinnaker, Vault, Consul \\
\textbf{Monitoring \& Observability\hspace{6pt}} & Datadog, Dynatrace, Prometheus, Grafana \\
\end{tabularx}

\section{Experience}
\headingBf{Company A}{2025 -- Present}
\headingIt{Site Reliability Engineer}{}
\begin{resume_list}
  \item Onboarded Kubernetes clusters to Dynatrace, reducing MTTD by 35\%.
  \item Implemented non-disruptive upgrades in AKS, improving uptime to 99.99\%.
  \item Led incident response and RCA, cutting resolution time by 40\%.
\end{resume_list}

\headingBf{Company B}{2024 -- 2025}
\headingIt{DevOps Engineer}{}
\begin{resume_list}
  \item Built GCP infrastructure using Terraform, automating provisioning for 100+ resources.
  \item Created Python scripts to validate secrets, reducing manual work by 90\%.
  \item Maintained SLIs/SLOs and ensured SLA compliance using Datadog.
\end{resume_list}

\headingBf{Company C}{2020 -- 2024}
\headingIt{DevOps Associate}{}
\begin{resume_list}
  \item Improved CI/CD pipeline efficiency by 25\% with ArgoCD image updater.
  \item Automated SonarQube setup using Python and REST APIs.
  \item Contributed to branching strategy and monitored systems 24/7 using Datadog.
\end{resume_list}

\section{Education}
\headingBf{XYZ University}{2016 -- 2020}
\headingIt{B.Tech in Computer Science}{GPA: 9.6/10}

\section{Certifications and Awards}
\begin{resume_list}
  \item Certified Kubernetes Administrator (CKA)
  \item Certified Kubernetes Application Developer (CKAD)
  \item Azure Fundamentals (AZ-900)
  \item Winner - Cloud Hackathon 2023
\end{resume_list}


\section{Publications}
\headingBf{AutoScale: Dynamic Resource Allocation for Microservices}{Dec 2023}
\begin{resume_list}
  \item Published in International Conference on Cloud Systems. Proposed a Kubernetes autoscaler using predictive algorithms for workload spikes.
\end{resume_list}

\headingBf{ObservaTrack: A Unified Observability Dashboard}{Jul 2022}
\begin{resume_list}
  \item Developed a centralized monitoring solution integrating Prometheus, Grafana, and alert systems; featured at DevOpsCon Europe.
\end{resume_list}

\end{document}

